Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-29 paper.tex
update

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increasing number of large-scale enterprise applications, the number of Web services has increased substantially and unprecedentedly. Therefore, \textit{manual and semi-automated web service compositions} are considered to be less efficient while \textit{automated web service composition} demands less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic dimension enables a better understanding and collaboration through ontology-based semantics \cite{o2005review}. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}, which make ``machine understanding'' possible through identifying and matching semantic similarities in input/output parameters of web services. The second challenge is related to finding optimised solutions in QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions associated with a single optimised QoS value.

Existing works on service composition focus mainly on addressing only one challenge above. Among these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow. This is generally considered as a \textit{semi-automated Web service composition} approach \cite{bahadori2009optimal,parejo2008qos}. Meanwhile, many research works consider the NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desired balance.

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality based on our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown its promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work:

\begin{enumerate}
 \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously to achieve a desirable balance on both sides.

 \item To propose a PSO-based service composition approach that utilises the proposed comprehensive quality model. To do that we optimise a queue of web services by evaluating the comprehensive quality of its decoded representations.

 \item To address a desirable balance that can be achieved using our comprehensive quality model, we conduct experiments to compare our proposed model with one widely used QoS model using PSO-based approach. In addition, to evaluate the effectiveness of our PSO-based approach,  we also compare one recent GP approach \cite{ma2015hybrid} with our PSO-based approach using our proposed model. Both comparisons utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}

\end{enumerate}

@@

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of desired task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. $(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desired balance of semantic matchmaking quality and QoS. To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desired trade-off of both quality aspects. In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.

>>>>

\textit{Web service composition} pertains to a chain of multiple web services to provide a value-added composition service that accommodates customers' complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems.

Two most notable challenges for web service composition are ensuring interoperability of services and achieving Quality of Service (QoS) optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge in syntactic and semantic dimensions. The syntactic dimension is covered by the XML-based technologies (such as $WSDL$, $SOAP$). The semantic dimension enables a better collaboration through ontology-based semantics. There are many ontology languages and formats for semantic service descriptions, such as OWL-S, WSML, and SAWSDL \cite{petrie2016web}. The second challenge is related to finding optimised solutions in QoS. This problem gives birth to \textit{QoS-aware service composition} that aims to find composition solutions with optimised QoS.

Existing works on service composition focus mainly on addressing only one challenge above. In these works, huge efforts have been devoted to optimise the quality of compositions under a pre-defined abstract workflow. This is generally considered as a \textit{semi-automated Web service composition} approach \cite{parejo2008qos}. Meanwhile, many research works consider a NP-hard problem of generating a composition plan automatically in discovering and selecting suitable web services \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition, the resources of semantic web services are described semantically to enable a better interoperability for chaining web services. In the past few years, substantial works have been done on semantic web service composition \cite{bansal2016generalized,boustil2014semantic,mier2015integrated}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously to achieve a desirable balance.

The overall goal of this paper is to \textit{develop a general comprehensive approach to automated QoS-aware semantic web service composition that satisfactorily optimises both QoS and semantic matchmaking quality}. Particularly, this paper extends existing works of QoS-aware service composition by considering jointly optimise QoS and semantic matchmaking quality using our proposed comprehensive quality model. Particle Swarm Optimisation (PSO) has shown promise in searching for near-optimised service composition solutions \cite{da2016particle}. We will propose a PSO-based service composition approach with explicit support for our proposed quality model. We will achieve three objectives in this work:

\begin{enumerate}
 \item To propose a general comprehensive quality model that addresses QoS and semantic matchmaking quality simultaneously with a desirable balance on both sides.

 \item To propose a PSO-based service composition approach using the proposed comprehensive quality model. To do that we optimise a service candidates queue by evaluating the comprehensive quality of its decoded representation.

 \item To address the effectiveness of our PSO-based approach and a desirable balance achieved using our comprehensive quality model, we first compare our PSO-based approach with one recent GP-based approach \cite{ma2015hybrid} using our proposed quality model, and then compare our proposed quality model with one widely used QoS model using our proposed PSO-based approach.
\end{enumerate}

@@

\textbf{Definition 1.} A request from users is defined as a composition task in a tuple: $Comp.T = \{I_{T}, O_{T}\}$ by giving a set of task inputs $I_{T}$ and expecting  a set of task outputs $O_{T}$, where $I_{T}$ and $O_{T}$ are associated with related concepts $I^{C}_{T}$ and $O^{C}_{T}$ respectively in an ontology $O = \{ C \mid I^{C}_{T}, O^{C}_{T}  \subseteq C \}$.

@@

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. Two objectives of this evaluation are to: $(1)$ measure the effectiveness of our PSO-based approach. To do this, we compare our PSO-based method with one existing GP-based approach \cite{ma2015hybrid}. $(2)$ measure the effectiveness of our proposed comprehensive quality model for achieving desirable balance of semantic matchmaking quality and QoS. To do this, we compare a widely used QoS model in QoS-aware web service composition \cite{ma2015hybrid,da2016particle,da2015graphevol} with our comprehensive quality model using our PSO-based approach.

@@

\section{Conclusion}\label{conclusion}
This work introduces a general comprehensive evaluation model for considering semantic matchmaking quality and QoS simultaneously. We proposed a PSO-based service composition approach utilising our proposed quality mode that can achieve a desirable trade-off of both quality aspects. In addtion, we compare one recent GP-approach with our PSO-based method to show our performance that results in finding more optimised solutions. Future works can investigate multi-objective EC techniques to produce a set of composition solutions for the situations when the quality preference is not known.
